\newacronym{arp}{ARP}{Address Resolution Protocol}

\newglossaryentry{BlueTeam}{
    name=Blue Team,
    description={The blue team is responsible for protective measures within an organization; during an exercise, they detect and defend against red team engagements.}
}

\newacronym{cli}{CLI}{Command Line Interface}

\newacronym{dhcp}{DHCP}{Dynamic Host Configuration Protocol}

\newacronym{dns}{DNS}{Domain Name System}

\newglossaryentry{GreenTeam}{
    name=Green Team,
    description={The green team represents the cooperation between the blue and yellow teams to close knowledge gaps in both areas.}
}

\newacronym{ids}{IDS}{Intrusion Detection System}

\newacronym{ips}{IPS}{Intrusion Prevention System}

\newacronym{mitm}{MITM}{Man-in-the-Middle}

\newglossaryentry{ProxyServer}{
  name=Proxy Server,
  description={An intermediary service between a client and a server.}
}

\newacronym{nsak}{NSAK}{Network Swiss Army Knife}

\newacronym{oci}{OCI}{Open Container Initiative}

\newglossaryentry{OrangeTeam}{
    name=Orange Team,
    description={The orange team represents the cooperation between the red and yellow teams, primarily for sharing insights, knowledge, and education.}
}

\newglossaryentry{PurpleTeam}{
    name=purple team,
    description={Purple teaming describes the cooperation between red and blue teams to enhance mutual understanding and defensive capabilities.}
}

\newglossaryentry{RedTeam}{
    name=red team,
    description={The red team consists of ethical hackers who simulate attacks against systems, networks, and software to test defensive measures.}
}

\newacronym{rogueap}{RAP}{Rogue Access Point}

\newacronym{siem}{SIEM}{Security Information and Event Management}

\newacronym{soc}{SOC}{Security Operations Center}

\newacronym{ssid}{SSID}{Service Set Identifier}

\newacronym{tcp}{TCP}{Transmission Control Protocol}

\newacronym{udp}{UDP}{User Datagram Protocol}

\newglossaryentry{WhiteTeam}{
    name=White Team,
    description={The white team consists of non-technical and technical stakeholders who provide oversight, compliance guidance, and organizational requirements during an exercise.}
}

\newglossaryentry{YellowTeam}{
    name=Yellow Team,
    description={The yellow team consists of system, network, and software architects and engineers who design and maintain the infrastructure.}
}

\newacronym{api}{API}{Application Programming Interface}

\newacronym{rest}{REST}{Representational State Transfer}

\newacronym{yaml}{YAML}{YAML Ain't Markup Language}

\newacronym{git}{GIT}{Git is a free and open source distributed version control system designed to handle everything from small to very large projects with speed and efficiency}

\newacronym{mac}{MAC}{Media Access Control}
